Clustering in a hyperbolic model of complex networks.

### 2020-03-12 clustering_infinite_model.tex
Removed several LaTeX warnings

\section{Clustering and the degree of the typical point in $\Ginf$\label{sec:Ginf}\label{sec:asymptotics_average_clustering_ast_P}}

@@

For any fixed value $y_0>0$, the set of points inside $\BallPo{y_0}$ is a Poisson process with intensity $f \cdot 1_{\BallPo{y_0}}$. As $\mu(\BallPo{y_0}) = \mu(y_0) = \xi e^{y_0/2} < \infty$, this can be described alternatively by first picking $N \isd \Po( \mu(y_0) )$ and then taking $N$ i.i.d.~points in $\BallPo{y_0}$ according to the probability density $f \cdot 1_{\BallPo{y_0}} / \mu(y_0)$. (That is, the intensity function of the Poisson point process, but set to zero outside of $\BallPo{y_0}$ and re-normalized in such a way that it integrates to one.) Hence, if we condition on the event that $y$ takes on some fixed value $y_0$ and that there are exactly $k$ points of $\Pcal$ inside $\BallPo{y_0}$, then those $k$ points behave like $k$ i.i.d.~points in $\BallPo{y_0}$ chosen according to the mentioned re-normalized probability density function. This shows that, for every $k\geq 2$:
\[
	\CExp{C}{D=k, y=y_0} 
	= \frac{1}{{k\choose 2}} \Ee\left( \sum_{1\leq i < j \leq k} \1_{\{u_i\in \BallPo{u_j}\}} \right)
	= \Exp{\1_{\{u_1\in\BallPo{u_2}\}}},
\]
where $u_1,\dots, u_n$ are i.i.d.~points in $\BallPo{y_0}$ with the above mentioned density.
Note that this does not depend on the value of $k$. For notational convenience, we will write 
\begin{equation}\label{eq:def_Py}
	P(y_0) := \Exp{\1_{\{u_1\in\BallPo{u_2}\}}},
\end{equation}
with $u_1, u_2$ as above.

@@

\subsubsection{Determining $P(y_0,y_1,y_2)$}

@@

\subsubsection{Integrating over $y_1, y_2$}

@@

Applying the change of variables $z_i := e^{-y_i/2}$, $i=1,2$, and Lemma~\ref{lem:triangle_prob_y_coordinates} gives 
\begin{align*}
	I_1(y_0) &=	4 (\alpha-1/2)^2 \cdot \int_{z_0>z_1>z_2>0} P(y_0,y_1(z),y_2(z)) z_1^{2\alpha-2} z_2^{2\alpha-2} 
		\dd z_2\dd z_1 \\
	&= 4 (\alpha-1/2)^2 \cdot \left( \int_{z_0>z_1>z_2>0} 1 \cdot z_1^{2\alpha-2} z_2^{2\alpha-2} 
		\dd z_2 \dd z_1 \right. \\
	&\hspace{10pt} \left. - \int_{{z_0>z_1>z_2>0,}\atop{z_0 < z_1+z_2}} G(z_0,z_1,z_2) \cdot z_1^{2\alpha-2} z_2^{2\alpha-2} 
		\dd z_2 \dd z_1 \right) \\
	&=: 4 (\alpha-1/2)^2 ( I_{11}(y_0) - I_{12}(y_0)). 
\end{align*}

@@

\begin{equation}\label{eq:def_Delta_P_computation_int_J_1}
	J_{a,b,c}(z_0) := z_0^a \int_{{z_0>z_1>z_2>0,}\atop{z_0 < z_1+z_2}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} \dd z_2\dd z_1.
\end{equation}
and note that
\begin{equation}\label{eq:Delta_P_computation_I12_with_J}
	I_{1,2}(y_0) = \frac{1}{4} (J_{0,-1,1}(z_0)+J_{0,1,-1}(z_0)+J_{2,-1,-1}(z_0)+2J_{0,0,0}(z_0)-2J_{1,-1,0}(z_0)-2J_{1,0,-1}(z_0)).
\end{equation}

@@

We will follow a similar strategy as for $I_1(y_0)$. First, using the change of variables $z_i := e^{-y_i/2}$, $i=1,2$,
we get
\begin{align*}
	I_2(y_0) &= 4 (\alpha-1/2)^2 \cdot \int_{1>z_1>z_2,z_0>0} P(y_0,y_1(z_1),y_2(z_2)) z_1^{2\alpha-2} z_2^{2\alpha-2} 
		\dd z_2 \dd z_1 \\
	&= 4 (\alpha-1/2)^2 \cdot \left( \int_{1>z_1>z_0,z_2>0}  z_0 z_1^{2\alpha-3} z_2^{2\alpha-2} 
		 \dd z_2 \dd z_1 \right. \\
	&\hspace{10pt}\left. - \int_{{1>z_1>z_0,z_2>0}\atop{z_1 < z_0+z_2}} G(z_1,z_0,z_2) z_0 z_1^{2\alpha-3} 	
		z_2^{2\alpha-2} \dd z_2 \dd z_1 \right) \\
	&=: 4 (\alpha-1/2)^2 (I_{21}(y_0) - I_{22}(y_0)). 
\end{align*}

@@

To deal with $I_{22}(y_0)$ we consider the function
\[
	J_{a,b,c}^\prime(z_0) := z_0^a \int_{{1>z_1>\max(z_0,z_2); z_0,z_2>0}\atop{z_1 < z_0+z_2}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} \dd z_2 \dd z_1
\]
and write
\begin{equation}\label{eq:Delta_P_computation_I22_J}
\begin{aligned}
		I_{2,2}(y_0) &= \frac{1}{4}\left(J_{0,-1,1}^\prime(z_0) + J_{2,-1,-1}^\prime(z_0)
		+ J_{0,1,-1}^\prime(z_0)\right) \\
		&\hspace{10pt}+ \frac{1}{2}\left( J_{1,-1,0}^\prime(z_0) - J_{0,0,0}^\prime(z_0) - J_{1,0,-1}^\prime(z_0)\right).
\end{aligned}
\end{equation}

@@

\subsubsection{Computing $\gamma$ and $\gamma(k)$\label{ssec:exact_expressions_clustering_P}}

@@

\subsubsection{Explicit expressions for $\gamma, \gamma(k)$ when $\alpha=1$.}\label{ssec:alphais1}

We've already established that $\gamma, \gamma(k)$ can be obtained at $\alpha=1$ by
taking the $\alpha\to 1$ limit of the expression obtained for $\alpha=1$. Here we derive an alternative explicit expression for completeness. This is what we will do in the current section.

>>>>

\section{Clustering and the degree of the typical point in \texorpdfstring{$\Ginf$}{G infinity}\label{sec:Ginf}\label{sec:asymptotics_average_clustering_ast_P}}

@@

For any fixed value $y_0>0$, the set of points inside $\BallPo{y_0}$ is a Poisson process with intensity $f \cdot 1_{\BallPo{y_0}}$. As $\mu(\BallPo{y_0}) = \mu(y_0) = \xi e^{y_0/2} < \infty$, this can be described alternatively by first picking $N \isd \Po( \mu(y_0) )$ and then taking $N$ i.i.d.~points in $\BallPo{y_0}$ according to the probability density $f \cdot 1_{\BallPo{y_0}} / \mu(y_0)$. (That is, the intensity function of the Poisson point process, but set to zero outside of $\BallPo{y_0}$ and re-normalized in such a way that it integrates to one.) Hence, if we condition on the event that $y$ takes on some fixed value $y_0$ and that there are exactly $k$ points of $\Pcal$ inside $\BallPo{y_0}$, then those $k$ points behave like $k$ i.i.d.~points in $\BallPo{y_0}$ chosen according to the mentioned re-normalized probability density function. This shows that, for every $k\geq 2$:
\[
	\CExp{C}{D=k, y=y_0} 
	= \frac{1}{\binom{k}{2}} \Ee\left( \sum_{1\leq i < j \leq k} \1_{\{u_i\in \BallPo{u_j}\}} \right)
	= \Exp{\1_{\{u_1\in\BallPo{u_2}\}}},
\]
where $u_1,\dots, u_n$ are i.i.d.~points in $\BallPo{y_0}$ with the above mentioned density.
Note that this does not depend on the value of $k$. For notational convenience, we will write 
\begin{equation}\label{eq:def_Py}
	P(y_0) := \Exp{\1_{\{u_1\in\BallPo{u_2}\}}},
\end{equation}
with $u_1, u_2$ as above.

@@

\subsubsection{Determining \texorpdfstring{$P(y_0,y_1,y_2)$}{P(y0,y1,y2)}}

@@

\subsubsection{Integrating over \texorpdfstring{$y_1, y_2$}{y1, y2}}

@@

Applying the change of variables $z_i := e^{-y_i/2}$, $i=1,2$, and Lemma~\ref{lem:triangle_prob_y_coordinates} gives 
\begin{align*}
	I_1(y_0) &=	4 (\alpha-1/2)^2 \cdot \int_{z_0>z_1>z_2>0} P(y_0,y_1(z),y_2(z)) z_1^{2\alpha-2} z_2^{2\alpha-2} 
		\dd z_2\dd z_1 \\
	&= 4 (\alpha-1/2)^2 \cdot \left( \int_{z_0>z_1>z_2>0} 1 \cdot z_1^{2\alpha-2} z_2^{2\alpha-2} 
		\dd z_2 \dd z_1 \right. \\
	&\hspace{10pt} \left. - \int_{\substack{{z_0>z_1>z_2>0,}\\{z_0 < z_1+z_2}}} G(z_0,z_1,z_2) \cdot z_1^{2\alpha-2} z_2^{2\alpha-2} 
		\dd z_2 \dd z_1 \right) \\
	&=: 4 (\alpha-1/2)^2 ( I_{11}(y_0) - I_{12}(y_0)). 
\end{align*}

@@

\begin{equation}\label{eq:def_Delta_P_computation_int_J_1}
	J_{a,b,c}(z_0) := z_0^a \int_{\substack{{z_0>z_1>z_2>0,}\\{z_0 < z_1+z_2}}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} \dd z_2\dd z_1.
\end{equation}
and note that
\begin{equation}\label{eq:Delta_P_computation_I12_with_J}
	I_{1,2}(y_0) = \frac{1}{4} (J_{0,-1,1}(z_0)+J_{0,1,-1}(z_0)+J_{2,-1,-1}(z_0)+2J_{0,0,0}(z_0)-2J_{1,-1,0}(z_0)-2J_{1,0,-1}(z_0)).
\end{equation}

@@

We will follow a similar strategy as for $I_1(y_0)$. First, using the change of variables $z_i := e^{-y_i/2}$, $i=1,2$,
we get
\begin{align*}
	I_2(y_0) &= 4 (\alpha-1/2)^2 \cdot \int_{1>z_1>z_2,z_0>0} P(y_0,y_1(z_1),y_2(z_2)) z_1^{2\alpha-2} z_2^{2\alpha-2} 
		\dd z_2 \dd z_1 \\
	&= 4 (\alpha-1/2)^2 \cdot \left( \int_{1>z_1>z_0,z_2>0}  z_0 z_1^{2\alpha-3} z_2^{2\alpha-2} 
		 \dd z_2 \dd z_1 \right. \\
	&\hspace{10pt}\left. - \int_{\substack{{1>z_1>z_0,z_2>0}\\{z_1 < z_0+z_2}}} G(z_1,z_0,z_2) z_0 z_1^{2\alpha-3} 	
		z_2^{2\alpha-2} \dd z_2 \dd z_1 \right) \\
	&=: 4 (\alpha-1/2)^2 (I_{21}(y_0) - I_{22}(y_0)). 
\end{align*}

@@

To deal with $I_{22}(y_0)$ we consider the function
\[
	J_{a,b,c}^\prime(z_0) := z_0^a \int_{\substack{{1>z_1>\max(z_0,z_2); z_0,z_2>0}\\{z_1 < z_0+z_2}}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} \dd z_2 \dd z_1
\]
and write
\begin{equation}\label{eq:Delta_P_computation_I22_J}
\begin{aligned}
		I_{2,2}(y_0) &= \frac{1}{4}\left(J_{0,-1,1}^\prime(z_0) + J_{2,-1,-1}^\prime(z_0)
		+ J_{0,1,-1}^\prime(z_0)\right) \\
		&\hspace{10pt}+ \frac{1}{2}\left( J_{1,-1,0}^\prime(z_0) - J_{0,0,0}^\prime(z_0) - J_{1,0,-1}^\prime(z_0)\right).
\end{aligned}
\end{equation}

@@

\subsubsection{Computing \texorpdfstring{$\gamma$}{gamma} and \texorpdfstring{$\gamma(k)$}{gamma(k)}\label{ssec:exact_expressions_clustering_P}}

@@

\subsubsection{Explicit expressions for \texorpdfstring{$\gamma, \gamma(k)$}{gamma, gamma(k)} when \texorpdfstring{$\alpha=1$}{alpha equals 1}.}\label{ssec:alphais1}

We've already established that $\gamma, \gamma(k)$ can be obtained at $\alpha=1$ by
taking the $\alpha\to 1$ limit of the expression obtained for $\alpha=1$. Here we derive an alternative explicit expression for completeness. Since the rest of our 
proofs do not the depend on it the reader could decide to skip this section on a first reading.

### 2020-03-12 hyperbolic_degrees.tex
Removed several LaTeX warnings

\section{Degrees when $k\to\infty$: proof of Theorem~\ref{thm:degrees_hyperbolic}\label{sec:degrees}}

@@

\subsection{Expected degrees in $\Gbox$ and $\GPo$}\label{ssec:expected_degrees_GPo}

@@

\subsection{Joint degrees in $\Gbox$ and $\GPo$}\label{ssec:joint_degrees_GPo}

>>>>

\section{Degrees when \texorpdfstring{$k\to\infty$}{k tends to infinity}: proof of Theorem~\ref{thm:degrees_hyperbolic}\label{sec:degrees}}

@@

\subsection{Expected degrees in \texorpdfstring{$\Gbox$}{G box} and \texorpdfstring{$\GPo$}{G Po}}\label{ssec:expected_degrees_GPo}

@@

\subsection{Joint degrees in \texorpdfstring{$\Gbox$}{G box} and \texorpdfstring{$\GPo$}{G Po}}\label{ssec:joint_degrees_GPo}

### 2020-03-12 introduction.tex
Removed several LaTeX warnings

We will study the other notion of clustering, the one which is also considered by Krioukov et al.~\cite{krioukov2010hyperbolic} and Gugelmann et al.~\cite{gugelmann2012random}. It is sometimes called the {\em local} clustering coefficient, although we should point out that Gugelmann et al.~actually call it the global clustering coefficient in their paper. For a graph $G$ and a vertex $v\in V(G)$ we define the clustering coefficient {\em of $v$} as:
\[
	c(v) := \left\{\begin{array}{cl}
		\displaystyle \frac{1}{{\text{deg}(v)\choose 2}} \sum_{u,w\sim v} 1_{\{uw \in E(G)\}}, 
			& \text{ if $\text{deg}(v) \geq 2$, }\\
		& \\
        0, & \text{ otherwise,}
        \end{array}\right.
\]
where $E(G)$ denotes the edge set of $G$ and $\text{deg}(v)$ is the degree of vertex $v$. That is, provided $v$ has degree at least two, $c(v)$ equals the number of edges that are actually present between the neighbours of $v$ divided by the number of edges that could possibly be present between the neighbours given the degree of $v$.
The clustering coefficient of $G$ is now defined as the average of $c(v)$ over all vertices $v$:
\[
	c(G) := \frac{1}{|V(G)|} \sum_{v\in V(G)} c(v).
\]

@@

In addition to the clustering coefficient, we shall also be interested in the {\em clustering function}.
This assigns to each non-negative integer $k$ the value
\begin{equation}\label{eq:def_clustering_function}
	c(k; G) := \begin{cases}
		\displaystyle \frac{1}{N(k)} \sum_{v \in V(G), \atop \text{deg}(v)=k}  c(v),  &\mbox{ if } N(k) \ge 1,\\
		0, &\mbox{else,}
	\end{cases}
\end{equation}
where $N(k)$ denotes the number of vertices of degree exactly $k$ in $G$. In other words, the clustering function assigns to the integer $k$ the average of the local clustering coefficient over all vertices of degree $k$. We remark that, while it might seem natural to consider $c(k)$ to be ``undefined'' when $N(k)=0$, we prefer to use the above definition for technical 
convenience.  This way $c(k; G(n;\alpha,\nu) )$ is a plain vanilla random variable and we can for instance compute its moments without any issues.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{figures/cn10000nu0512rep100a05to5Squares.pdf}
    \caption{Plot of $\gamma$ for $\alpha$ varying from $0.5$ to $5$ on the horizontal axis and 
    for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green). Simulations (squares in corresponding colour) with $n=10000$ and $100$ repetitions.\label{fig:gamma}}
\end{figure}

@@

\noindent
A plot of $\gamma(k)$,  together with the results of computer experiments, can be found in Figure~\ref{fig:gammak}. %
%
%
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{figures/ckn10000a08nu0512rep100k2to25Squares.pdf}
    \caption{Plot $\gamma(k)$ for $k$ varying from 2 to 25 on the horizontal axis, for $\alpha=0.8$ and $\nu=\frac{1}{2}$ 
    (blue), $\nu=1$ (purple), $\nu=2$ (green). Simulations (squares in corresponding colour) with $n=10000$ and $100$ repetitions.\label{fig:gammak}}
\end{figure}%
%
Again, we remark that the above expression for $\gamma(k)$ appears to have a singularity at $\alpha=1$, but this will turn out to be a removable singularity. 
Again, we have not been able to find a closed form expression in terms of standard functions in the case when $\alpha=1$, but in 
Section~\ref{ssec:alphais1} we do provide an explicit expression involving integrals.

@@

\subsubsection{Scaling of $\gamma(k)$}

@@

\subsubsection{The degree distribution and the range of $k_n$ in Theorem~\ref{thm:mainktoinfty}}

@@

\subsubsection{Transition in scaling at $\alpha = 3/4$.}

>>>>

We will study the other notion of clustering, the one which is also considered by Krioukov et al.~\cite{krioukov2010hyperbolic} and Gugelmann et al.~\cite{gugelmann2012random}. It is sometimes called the {\em local} clustering coefficient, although we should point out that Gugelmann et al.~actually call it the global clustering coefficient in their paper. For a graph $G$ and a vertex $v\in V(G)$ we define the clustering coefficient {\em of $v$} as:
\[
	c(v) := \left\{\begin{array}{cl}
		\displaystyle \frac{1}{\binom{\text{deg}(v)}{2}} \sum_{u,w\sim v} 1_{\{uw \in E(G)\}}, 
			& \text{ if $\text{deg}(v) \geq 2$, }\\
		& \\
        0, & \text{ otherwise,}
        \end{array}\right.
\]
where $E(G)$ denotes the edge set of $G$ and $\text{deg}(v)$ is the degree of vertex $v$. That is, provided $v$ has degree at least two, $c(v)$ equals the number of edges that are actually present between the neighbours of $v$ divided by the number of edges that could possibly be present between the neighbours given the degree of $v$.
The clustering coefficient of $G$ is now defined as the average of $c(v)$ over all vertices $v$:
\[
	c(G) := \frac{1}{|V(G)|} \sum_{v\in V(G)} c(v).
\]

@@

In addition to the clustering coefficient, we shall also be interested in the {\em clustering function}.
This assigns to each non-negative integer $k$ the value
\begin{equation}\label{eq:def_clustering_function}
	c(k; G) := \begin{cases}
		\displaystyle \frac{1}{N(k)} \sum_{\substack{v \in V(G), \\ \text{deg}(v)=k}}  c(v),  &\mbox{ if } N(k) \ge 1,\\
		0, &\mbox{else,}
	\end{cases}
\end{equation}
where $N(k)$ denotes the number of vertices of degree exactly $k$ in $G$. In other words, the clustering function assigns to the integer $k$ the average of the local clustering coefficient over all vertices of degree $k$. We remark that, while it might seem natural to consider $c(k)$ to be ``undefined'' when $N(k)=0$, we prefer to use the above definition for technical 
convenience.  This way $c(k; G(n;\alpha,\nu) )$ is a plain vanilla random variable and we can for instance compute its moments without any issues.

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[scale=0.6]{figures/cn10000nu0512rep100a05to5Squares.pdf}
    \caption{Plot of $\gamma$ for $\alpha$ varying from $0.5$ to $5$ on the horizontal axis and 
    for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green). Simulations (squares in corresponding colour) with $n=10000$ and $100$ repetitions.\label{fig:gamma}}
\end{figure}

@@

\noindent
A plot of $\gamma(k)$,  together with the results of computer experiments, can be found in Figure~\ref{fig:gammak}. %
%
%
\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.6]{figures/ckn10000a08nu0512rep100k2to25Squares.pdf}
    \caption{Plot $\gamma(k)$ for $k$ varying from 2 to 25 on the horizontal axis, for $\alpha=0.8$ and $\nu=\frac{1}{2}$ 
    (blue), $\nu=1$ (purple), $\nu=2$ (green). Simulations (squares in corresponding colour) with $n=10000$ and $100$ repetitions.\label{fig:gammak}}
\end{figure}%
%
Again, we remark that the above expression for $\gamma(k)$ appears to have a singularity at $\alpha=1$, but this will turn out to be a removable singularity. 
Again, we have not been able to find a closed form expression in terms of standard functions in the case when $\alpha=1$, but in 
Section~\ref{ssec:alphais1} we do provide an explicit expression involving integrals.

@@

\subsubsection{Scaling of \texorpdfstring{$\gamma(k)$}{gamma(k)}}

@@

\subsubsection{The degree distribution and the range of \texorpdfstring{$k_n$}{kn} in Theorem~\ref{thm:mainktoinfty}}

@@

\subsubsection{Transition in scaling at \texorpdfstring{$\alpha = 3/4$}{alpha equals 3/4}.}

### 2020-03-12 preliminaries.tex
Removed several LaTeX warnings

\subsection{The infinite limit model $\Ginf$\label{ssec:infinite_model}}

@@

\subsection{The finite box model $\Gbox$\label{ssec:finite_model}}

@@

\subsection{The Poissonized KPKVB model $\GPo$}

@@

\subsection{Coupling $\GPo$ and $\Gbox$\label{ssec:coupling_H_P}}

@@

\begin{equation}\label{eq:def_campbell_mecke}
\begin{array}{c}
\displaystyle	\Exp{\sum_{p_1, \dots, p_k \in \Pcal, \atop \text{distinct}} h(p_1, \dots, p_k, \Pcal)} \\
= \\
\displaystyle \int_{\mathcal{M}} \dots \int_{\mathcal{M}} \Exp{h(x_1,\dots, x_k, \Pcal\cup\{x_1,\dots,x_k\})} \mu(dx_1)\dots\mu(dx_k).
\end{array}
\end{equation}

>>>>

\subsection{The infinite limit model \texorpdfstring{$\Ginf$}{G infinity}\label{ssec:infinite_model}}

@@

\subsection{The finite box model \texorpdfstring{$\Gbox$}{G box}\label{ssec:finite_model}}

@@

\subsection{The Poissonized KPKVB model \texorpdfstring{$\GPo$}{G Po}}

@@

\subsection{Coupling \texorpdfstring{$\GPo$}{G Po} and \texorpdfstring{$\Gbox$}{G box}\label{ssec:coupling_H_P}}

@@

\begin{equation}\label{eq:def_campbell_mecke}
\begin{array}{c}
\displaystyle	\Exp{\sum_{\substack{p_1, \dots, p_k \in \Pcal, \\ \text{distinct}}} h(p_1, \dots, p_k, \Pcal)} \\
= \\
\displaystyle \int_{\mathcal{M}} \dots \int_{\mathcal{M}} \Exp{h(x_1,\dots, x_k, \Pcal\cup\{x_1,\dots,x_k\})} \mu(dx_1)\dots\mu(dx_k).
\end{array}
\end{equation}

### 2020-03-12 proofs_finite_k.tex
Removed several LaTeX warnings

\subsection{Clustering function for fixed $k$, proving Theorem~\ref{thm:mainkfixed}}

@@

$$ \begin{array}{rcl} 
|c(k; G)-c(k;H)| 
& = & \displaystyle
\left| \sum_{v\in V(G), \atop\text{deg}_G(v)=k} \frac{c_G(v)}{N_G(k)} - 
\sum_{v\in V(H), \atop\text{deg}_{H}(v)=k} \frac{c_{H}(v)}{N_{H}(k)} \right| \\[8ex]
& = & \displaystyle 
\left| \frac{1}{N_G(k)} \left( \sum_{v\in V(G)\setminus V(H), \atop\text{deg}_G(v)=k} c_G(v)
+ \sum_{v\in V(G)\cap V(H), \atop{\text{deg}_G(v)=k, \atop\text{deg}_{H}(v)\neq k}} c_G(v) \right) \right. \\
& & \displaystyle
- \frac{1}{N_{H}(k)} \left(\sum_{v\in V(H)\setminus V(G), \atop\text{deg}_{H}(v)=k} c_{H}(v)
+ \sum_{v\in V(G)\cap V(H), \atop{\text{deg}_G(v)\neq k, \atop\text{deg}_{H}(v)=k}} c_{H}(v) \right) \\
& & \displaystyle  
\left. + \left(\frac{1}{N_G(k)}-\frac{1}{N_{H}(k)} \right) \cdot 
\left( \sum_{v \in V(G)\cap V(H), \atop\text{deg}_G(v)=\text{deg}_{H}(v)=k}
c_G(v) \right) \right| \\[8ex]
 & \leq & \displaystyle
 \frac{2|E(G)\Delta E(H)|}{N_G(k)} + \frac{2|E(G)\Delta E(H)|}{N_{H}(k)} + 
 \frac{|N_{H}(k) - N_G(k)|}{N_G(k)\cdot N_{H}(k)} \cdot N_{H}(k) \\[5ex]
 & = & \displaystyle 
 \frac{2|E(G)\Delta E(H)|}{N_G(k)} + \frac{2|E(G)\Delta E(H)|}{N_{H}(k)} + \frac{|N_{H}(k) - N_G(k)|}{N_G(k)} \\[5ex]
 & \leq & \displaystyle
 \frac{2|E(G)\Delta E(H)|}{N_G(k)} + \frac{2|E(G)\Delta E(H)|}{N_{H}(k)} + \frac{2|E(G)\Delta E(H)|}{N_G(k)} \\[5ex]
 & \leq & \displaystyle
\frac{6 |E(G)\Delta E(H)|}{N_G(k)-2|E(G)\Delta E(H)|}.
\end{array} $$

@@

$$ c(k; G_n)-c(k; \GPo) \xrightarrow[n\to\infty]{\Pee} 0, $$

%\noindent
%for every fixed $k\geq 2$.
\end{corollary}

Since $N_{G_n}(k) - 2|E(G_n)\Delta E(\GPo)| \leq N_{\GPo}(k) \leq N_{G_n}(k) + 2|E(G_n)\Delta E(\GPo)|$ for all $k\geq 1$,
we can also conclude from~\eqref{eq:gugeldegseqaap} and Lemma~\ref{lem:NDGnGPo} that:

\begin{corollary}\label{cor:NGPok} 
For every fixed $k\geq 0$ we have

$$ \frac{N_{\GPo}(k)}{n} \xrightarrow[n\to\infty]{\Pee} \pmf(k). $$

@@

\noindent
(The case $k=0$ follows from all the other cases together with the fact that the $\pmf(k)$ sum to one.)

@@

Analogously to Corollaries~\ref{cor:pok} and~\ref{cor:NGPok} we obtain:

\begin{corollary}\label{cor:GPoHdegseq}
For every fixed $k$ we have

$$\frac{N_{\GboxH}(k)}{n} \xrightarrow[n\to\infty]{\Pee} \pmf(k). $$

@@

$$c(k;\GPo) - c(k;\GboxH) \xrightarrow[n \rightarrow \infty]{\Pee} 0. $$

@@

In combination with Corollary~\ref{cor:GPoHdegseq} we can conclude that

>>>>

\subsection{Clustering function for fixed \texorpdfstring{$k$}{k}, proving Theorem~\ref{thm:mainkfixed}}
%=======
%\subsection{Clustering function, proving Theorem~\ref{thm:mainkfixed}}
%In this subsection, we want to show that the clustering function of the KPKVB model $c(k; G(n;\alpha,\nu)) \xrightarrow{\Pee} \gamma(k)$ for any fixed $k$. The key idea is that for the poissonized KPKVB model the coupling with the box model is guaranteed to be exact (in the sense that it also preserves edges) for all vertices up to height $H = \frac{R}{4}$ (which is all we need to show the convergence of the clustering function for constant $k$).
%>>>>>>> Stashed changes

@@

$$ \begin{array}{rcl} 
|c(k; G)-c(k;H)| 
& = & \displaystyle
\left| \sum_{\substack{v\in V(G), \\ \text{deg}_G(v)=k}} \frac{c_G(v)}{N_G(k)} - 
\sum_{\substack{v\in V(H), \\ \text{deg}_{H}(v)=k}} \frac{c_{H}(v)}{N_{H}(k)} \right| \\[8ex]
& = & \displaystyle 
\left| \frac{1}{N_G(k)} \left( \sum_{\substack{v\in V(G)\setminus V(H), \\ \text{deg}_G(v)=k} } c_G(v)
+ \sum_{\substack{v\in V(G)\cap V(H), \\ \text{deg}_G(v)=k, \\ \text{deg}_{H}(v)\neq k}} c_G(v) \right) \right. \\
& & \displaystyle
- \frac{1}{N_{H}(k)} \left(\sum_{\substack{ v\in V(H)\setminus V(G), \\ \text{deg}_{H}(v)=k} } c_{H}(v)
+ \sum_{\substack{v\in V(G)\cap V(H), \\ \text{deg}_G(v)\neq k, \\ \text{deg}_{H}(v)=k}} c_{H}(v) \right) \\
& & \displaystyle  
\left. + \left(\frac{1}{N_G(k)}-\frac{1}{N_{H}(k)} \right) \cdot 
\left( \sum_{\substack{v \in V(G)\cap V(H), \\ \text{deg}_G(v)=\text{deg}_{H}(v)=k}}
c_G(v) \right) \right| \\[8ex]
 & \leq & \displaystyle
 \frac{2|E(G)\Delta E(H)|}{N_G(k)} + \frac{2|E(G)\Delta E(H)|}{N_{H}(k)} + 
 \frac{|N_{H}(k) - N_G(k)|}{N_G(k)\cdot N_{H}(k)} \cdot N_{H}(k) \\[5ex]
 & = & \displaystyle 
 \frac{2|E(G)\Delta E(H)|}{N_G(k)} + \frac{2|E(G)\Delta E(H)|}{N_{H}(k)} + \frac{|N_{H}(k) - N_G(k)|}{N_G(k)} \\[5ex]
 & \leq & \displaystyle
 \frac{2|E(G)\Delta E(H)|}{N_G(k)} + \frac{2|E(G)\Delta E(H)|}{N_{H}(k)} + \frac{2|E(G)\Delta E(H)|}{N_G(k)} \\[5ex]
 & \leq & \displaystyle
\frac{6 |E(G)\Delta E(H)|}{N_G(k)-2|E(G)\Delta E(H)|}.
\end{array} $$

@@

$$ c(k; G_n)-c(k; \GPo) \xrightarrow[n\to\infty]{\Pee} 0, \quad\text{ and }\quad
\frac{N_{\GPo}(k)}{n} \xrightarrow[n\to\infty]{\Pee} \pmf(k). $$

@@

\noindent
(For the second statement we use that $N_{G_n}(k) - 2|E(G_n)\Delta E(\GPo)| \leq N_{\GPo}(k) \leq N_{G_n}(k) + 2|E(G_n)\Delta E(\GPo)|$.)

@@

Analogously to Corollary~\ref{cor:pok} we obtain:

@@

$$c(k;\GPo) - c(k;\GboxH) \xrightarrow[n \rightarrow \infty]{\Pee} 0, \quad\text{ and }\quad  
\frac{N_{\GboxH}(k)}{n} \xrightarrow[n\to\infty]{\Pee} \pmf(k). $$

@@

In combination with Corollary~\ref{cor:GPoGboxH} (second limit) we can conclude that

### 2020-03-12 proofs_infinite_k.tex
Removed several LaTeX warnings

\section{Clustering when $k\to\infty$ : overview of the proof strategy}

@@

\subsection{Coupling of local clustering between $\GPo$ and $\Gbox$}

>>>>

\section{Clustering when \texorpdfstring{$k\to\infty$}{k tends to infinity} : overview of the proof strategy}

@@

\subsection{Coupling of local clustering between \texorpdfstring{$\GPo$}{G Po} and \texorpdfstring{$\Gbox$}{G box}}

### 2020-03-12 transition.tex
Removed several LaTeX warnings

\section{From $\Gbox$ to $\Ginf$ (Proving Proposition \ref{prop:convergence_average_clustering_P_n})}\label{sec:clustering_Pn_to_P}

@@

\subsection{Comparing triangles between $\Ginf$ and $\Gbox$}

>>>>

\section{From \texorpdfstring{$\Gbox$}{G box} to \texorpdfstring{$\Ginf$}{G infinity} (Proving Proposition \ref{prop:convergence_average_clustering_P_n})}\label{sec:clustering_Pn_to_P}

@@

\subsection{Comparing triangles between \texorpdfstring{$\Ginf$}{G infinity} and \texorpdfstring{$\Gbox$}{G box}}
